Manuscript

### 2014-09-01 inst/simulation/manuscript.Rmd
...

```{r figure-2-init}
getSurveyRouteLocations = function(scenarios, modelName, iterations, years) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, years) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- SimulatedSmoothModelSpatioTemporal(study=study, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    surveyRoutes <- data.frame(estimates$getUnscaledObservationCoordinates(), Intersection=subset(estimates$data, year %in% years)$intersections>0)
    surveyRoutes$Scenario <- x$scenario
    surveyRoutes$Iteration <- x$iteration
    return(surveyRoutes)
  }, modelName=modelName, years=years)
}

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, year0, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- SimulatedSmoothModelSpatioTemporal(study=study, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()

@@

```{r figure-2}
iterations <- as.integer(c(1,1,3,2,5,6))
#iterations <- as.integer(c(1,1,3,2,5,7))
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations, years=2001)
surveyRoutes <- rbind(surveyRoutes[surveyRoutes$Intersection == FALSE,], surveyRoutes[surveyRoutes$Intersection == TRUE,])
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations, years=2001)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=2001, sd=F)
densitiesScaled <- ddply(densities, .(scenario), function(x) { x$X2001 <- scale(x$X2001); return(x) })
limits <- extent(study$studyArea$boundary)

#p <- ggplot(boundaryDF) + geom_polygon(aes(long, lat, group=group), fill=terrain.colors(100)[1]) +
p <- ggplot(densitiesScaled) + geom_raster(aes(x, y, fill=X2001)) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black")) + 
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal()
print(p)
saveFigure(p, "manuscript-figure-2a.png", width=8)

@@

p <- ggplot(populationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) + stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("darkgray","black"), labels=c("T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") + facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3.png", width=8, height=4)
```

```{r table-1}
ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2))
})
```

>>>>

```{r figure-2-init}
getSurveyRouteLocations = function(scenarios, modelName, iterations, years) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, years) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration) 
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    intersections <- subset(estimates$data, year %in% years)$intersections>0
    surveyRoutes <- data.frame(estimates$getUnscaledObservationCoordinates(), Intersection=intersections)
    surveyRoutes$Scenario <- x$scenario
    surveyRoutes$Iteration <- x$iteration
    return(surveyRoutes)
  }, modelName=modelName, years=years)
}

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, year0, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()

@@

```{r figure-2-test}
iterations <- as.integer(c(1,1,3,2,5,6))
year <- 2010
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios[1], modelName=modelNames[1], iterations=iterations[1], years=year)
surveyRoutes <- rbind(surveyRoutes[surveyRoutes$Intersection == FALSE,], surveyRoutes[surveyRoutes$Intersection == TRUE,])
agents <- getAgentLocations(scenarios=scenarios[1], modelName=modelNames[1], iterations=iterations[1], years=year)
densityST <- getEstimatedDensity(scenarios[1], modelNames[1], iterations[1], year=year, sd=FALSE)
densityFMP <- getEstimatedDensity(scenarios[1], modelNames[3], iterations[1], year=year, sd=FALSE)
limits <- extent(study$studyArea$boundary)

p <- ggplot(densityST) + geom_raster(aes_string(x="x", y="y", fill=paste0("X", year))) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black")) + 
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal()
print(p)
saveFigure(p, "tmp_compare_densities_ST.png", width=8)

p <- ggplot(densityFMP) + geom_raster(aes_string(x="x", y="y", fill=paste0("X", year))) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black")) + 
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal()
print(p)
saveFigure(p, "tmp_compare_densities_FMP.png", width=8)
```

```{r figure-2}
iterations <- as.integer(c(1,1,3,2,5,6))
#iterations <- as.integer(c(1,1,3,2,5,7))
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
surveyRoutes <- rbind(surveyRoutes[surveyRoutes$Intersection == FALSE,], surveyRoutes[surveyRoutes$Intersection == TRUE,])
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, sd=F)
# TODO: do not use scaling??
densitiesScaled <- ddply(densities, .(scenario), function(x, yearLayer) { x[,yearLayer] <- scale(x[,yearLayer]); return(x) }, yearLayer=yearLayer)
limits <- extent(study$studyArea$boundary)

#p <- ggplot(boundaryDF) + geom_polygon(aes(long, lat, group=group), fill=terrain.colors(100)[1]) +
p <- ggplot(densitiesScaled) + geom_raster(aes_string(x="x", y="y", fill=yearLayer)) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black")) + 
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal()
print(p)
saveFigure(p, "manuscript-figure-2a.png", width=8)

@@

p <- ggplot(populationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) + stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") + facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3.png", width=8, height=4)
```

```{r table-1}
ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2))
})
```
